\paperTitle

### 2014-05-13 doc/icml2014/exclusive-views.tex
Minor edits to lemma 2 proof

\begin{proof}
By the canonical reduction (\lemmaref{reduction}), we can assume without
  loss of generality that all observed variables are leaves and thus
  all v-structures are active.
Combined with the faithful representation assumption, this lets us
  reason about independences solely in terms of graph connectivity.

Let $h_0$ be a hidden variable in the clique $\sC$ and let $x_1, x_2$ be any
  two conditionally independent observed variables. 
Recall that if $x_1$ is an exclusive view of $h_0$ in $\sC$,
  then, conditioned on $h_0$, $x_1$ is independent of every other variable $h_i
  \in \sC$.
% Since $x_1 \perp x_2 \given h_0$, every path from $x_1$ to $x_2$ must go through $h_0$. 
Suppose neither $x_1$ nor $x_2$ are exclusive views for $h_0$, 
  then there exists some $h_1, h_2 \in \sC$ that $x_1, x_2$ are respectively dependent on.
However, $h_1$ and $h_2$ are connected by participation in the clique; consequently there is a path $x_1 \to h_1 \to h_2 \to x_2$. 
By \assumptionref{ci}, this implies that $x_1$ and $x_2$ are not
  independent conditioned on $h_0$, which is a contradiction.

>>>>

\begin{proof}
%By the canonical reduction (\lemmaref{reduction}), we can assume without
%  loss of generality that all observed variables are leaves and thus
%  all v-structures are active.
The faithful representation assumption lets us
  reason about independences solely in terms of graph connectivity.
\todo{v-structures no longer matter because of the assumption.
Does this need to be explained?}

Let $h_0$ be a hidden variable in the clique $\sC$ and let $x_1, x_2$ be any
  two conditionally independent observed variables. 
Recall that if $x_1$ is an exclusive view of $h_0$ in $\sC$,
  then, conditioned on $h_0$, $x_1$ is independent of every other variable $h_i
  \in \sC$.
% Since $x_1 \perp x_2 \given h_0$, every path from $x_1$ to $x_2$ must go through $h_0$. 
Suppose neither $x_1$ nor $x_2$ are exclusive views for $h_0$, 
  then there exists some $h_1, h_2 \in \sC$ that $x_1, x_2$ are respectively dependent on.
However, $h_1$ and $h_2$ are connected by participation in the clique; consequently there is an active trail $x_1 - h_1 - h_2 - x_2$. 
By \assumptionref{ci}, this implies that $x_1$ and $x_2$ are not
  independent conditioned on $h_0$, which is a contradiction.
